Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
clarificatino

However, we are not so much interested in the ability of the CCLM to
precisely model the language used in a community.

We now turn our interest to language-model-based community classifiers
(LMCC). Given a message $m$, and LMCC gives the probability that it
belongs in a community $c_i$ Using the Bayes theorem, we can turn a
CCLM into a LMCC. Indeed, the probability that a given message $m$
belongs to a community $c_i$ can be calculated as follows:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]
In the above,
$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ is given by the CCLM. $P(m)$ is our normalisation factor, which can be set so that
\[\sum_i P(c=c_i | m) = 1\].

Knowing that $m$ \emph{actually} comes from community $c_j$, we can
measure the precision our classifier, as a confusion matrix $C$,
which can be calculated as follows for a given set of messages (TODO: what set exactly?)
\[C_{ij} = average_{m \in Messages(c_j)}(P(c=c_i | m))\].

>>>>

% However, we are not so much interested in the ability of the CCLM to precisely model the language used in a community.

We now turn our interest to the Bayesian classifier induced by a CCLM, which we call a language-model-based community classifier
(LMCC). Indeed, the purpose of an LMCC is to estimate the probability $P(m|c_i)$ that a message $m$
belong in a community $c_i$. Using the Bayes theorem, we can turn a
CCLM into a LMCC: the probability that a given message $m$
belongs to a community $c_i$ can be calculated as follows:
\[P(c=c_i | m) = P(m | c_i)\frac {P(m)} {P(c=c_i)}\]
In the above,
$P(c=c_i)$ is the frequency of community $c_i$ in the dataset, and
$P(m | c_i)$ is given by the CCLM. $P(m)$ is the absolute
probability of a message, which can be computed as
\[P(m) = \frac 1 {\sum_i P(c=c_i) P(m|c=c_i ) }\].

We can characterise the quality the LMCC by a confusion matrix
$C$, defined by $C_{ij} = P(c=c_i | m)$ for a random message $m$ in
community $c_j$.  That is:
\[C_{ij} = average_{m \in Messages(c_j)}(P(c=c_i | m))\].
\jp{Is this test set or training set?}
